Viscous Transport in Eroding Porous Media

### 2019-07-30 docs/transport/erosion_transport.tex
working on quadrature section

\input{preambles.tex}
\begin{document}

@@

Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
integral by first finding boundary data of $v$.  We assume that $\Omega$
is a simply-connected interior domain.  Analogous formulas exist for
exterior domains, and for multiply-connected domains, $\bd\Omega$ is
simply decomposed into its different connected components.  The boundary
data of $v$ satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
Since $v$ is a holomorphic function and we have its boundary data, by
the Cauchy integral theorem we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.

In equation~\eqref{eqn:cauchy}, $v(x)$ depends on the density function
$\eta \in \CC$, so we use the notation $v[\eta](x)$ to denote the
holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
the derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  Having
introduced this notation, the two components of the Stokes double-layer
potential are~\cite{bar-wu-vee2015}
\begin{equation}
  \begin{aligned}
    u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
             -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
    u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
         +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
  \end{aligned}
  \label{eqn:cauchy1}
\end{equation}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation for the Gradient of the
Double-Layer Potential}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In addition to the velocity, we require a complex-valued representation
of the gradient of the velocity so that we can compute the shear stress
and the vorticity.  Each term of the gradient of the velocity field can
be written in terms of Cauchy integrals.  Taking the derivatives of
equation~\eqref{eqn:cauchy1} with respect to $x_1$ and $x_2$, we have 
\begin{align}
  \pderiv{u_1}{x_1} &= +\Re (v'[\tau_1](x)) + 
    \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
  \pderiv{u_1}{x_2} &= - \Im (v'[\tau_1](x)) - 
    \Im (v''[y\cdot\eta](x)) + x_1\Im (v''[\eta_1](x)) - 
    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_1} &= +\Re (v'[\tau_2](x)) - 
    \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
    x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_2} &= -\Im (v'[\tau_2](x)) - 
    \Re (v''[y\cdot\eta](x)) + x_1\Re (v''[\eta_1](x)) +
    \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
\end{align}
With these four expressions, the deformation tensor of the double-layer
potential, $\ssigma^D = \frac{1}{2} (\nabla \uu + \nabla \uu^T)$, is
written in terms of Cauchy integrals.  In addition, the vorticity is
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
 + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)).
\end{align}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Barycentric quadrature rule developed by Barnett et
al.~\cite{bar-wu-vee2015} approximates the double-layer potential for
the velocity~\eqref{eqn:stokesDLP} with bounded error.  However, to
compute the shear stress and vorticity, the method must be extended.  We
first briefly describe the original Barycentric quadrature method, and
then derive a necessary extension to simulate erosion.  We present the
quadrature for a simply-connected domain $\Omega$, and the method
naturally extends to the eroding geometry by applying the quadrature to
each of its connected component.  The method starts with an underlying
quadrature rule, and we use the trapezoid rule because of its superior
accuracy for smooth periodic functions~\cite{tre-wei2014}.  Since the
quadrature points are uniformly distributed, the quadrature weights are
$w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.

We next identify all the discretization points, the normal vector, and
the density function with their complex-value counterparts.  Then, all
the layer potentials are a combination of a Cauchy integral and its
first two derivatives.  Given a density function $\tau(y)$, the boundary
data is solved using the Sokhotski-Plemelj jump
relation~\eqref{eqn:SPrelation}.  If $x \in \Omega$ is too close to
$\bd\Omega$ and the trapezoid rule is applied to the identity
\begin{align}
  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
  \quad x \in \Omega,
\end{align}
the quadrature error is large since the integrand has a large
derivative.  However, if the trapezoid rule is applied to
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
\end{align}
the quadrature error is bounded since the integrand and all its
derivatives are bounded with respect to $x$. That is,
\begin{align}
  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0.
\end{align}
Rearranging for $v(x)$, we have
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}.
  \label{eqn:Baryv}
\end{align}
\todo[inline]{Need to cite~\cite{ioa-pap-per1991}.  They write formulas
for $v''(x)$ in this paper.  Need to be clear wrt what we did and what
  others have done} 
To approximate $v'(x)$, the trapezoid rule is applied to the two
integrals in the identity
\begin{align}
  v'(x) = \frac{\int\limits_{\bd\Omega} 
    \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
  {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy},
\end{align}
resulting in the quadrature rule
\begin{align}
  v'(x) \approx \frac{\sum\limits_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
  \label{eqn:Baryvprime}
\end{align}

To compute the shear stress and vorticity, we require a Barycentric
quadrature rule for $v''(x)$.  Mimicking the construction of the
quadrature rule for $v(x)$ and $v'(x)$, we start with the second
derivative of the Cauchy integral theorem
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x).
\end{align}
Using the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n > 1, \\
    \end{array}
  \right.
\end{align}
where $x \in \Omega$ and $n \in \mathbb{N}$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
This integrand is constructed so that it is bounded for all $x \in
\Omega$, and applying the trapezoid rule, we have
\begin{align}
  0 \approx  \sum_{j=1}^{N} 
      \frac{2v^{-}(y_j) - v''(x)(y_j-x)^2 - 2v(x) - 2(y_j-x)v'(x)}
      {(y_j-x)^3} w_j,
\end{align}
where the accuracy is independent of the proximity of $x$ to
$\bd\Omega$. Solving for $v''(x)$, the Barycentric quadrature rule for
the second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
\end{align}
This formula requires accurate approximations of $v(x)$ and $v'(x)$, but
these are available in equations~\eqref{eqn:Baryv}
and~\eqref{eqn:Baryvprime}.

To apply the quadrature to multiply-connected domains, we must all
consider exterior points $x \in \Omega^c$.  Mimicking the construction
in~\cite{bar-wu-vee2015}, we use the quadrature rule
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x} dy, 
\end{align}
is used, and the resulting Barycentric quadrature formula is
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
\end{align}
Again, values of $v(x)$ and $v'(x)$ are required, and these are
available in~\cite{bar-wu-vee2015}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Streamlines and Tortuosity}
\label{s:streamlines}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Having developed numerically accurate methods to compute the velocity
$\uu$ at points close to the bodies, we are able to compute the
trajectories of particles passing through an eroded body.  To find the
trajectory governed by equation~\eqref{eqn:trajectories}, we use the
fourth-order explicit Runge-Kutta method with a fixed time step size.
Since our method is both high-order in time and space, we are able to
simulate dynamics very close to the eroding bodies (Figure~\ref{fig:}
\todo[inline]{reference a figure or two from the results section)}.
Resolving the flow in these small velocity regions is essential to
accurately describe anomalous diffusion and
mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather a pressure drop boundary condition,
we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  In their experiment, Mitchell and Spagnolie place
the center of the eroding body $1.5$ times the body's radius above the
solid wall.  By using the numerical integration scheme described in
Section~\ref{s:method}, the eroding body can be placed much closer to
the solid wall.  In the following experiments, we consider an eroding
body that is initially a circle of radius $r=0.4$ and is placed near the
no-slip wall at $y=-1$.  We discretize the eroding body with
$N_\iin=256$ discretization points, and the center of the eroding body
is initially placed at $h/2$, $h/4$, and $h/10$, where $h = 2\pi
r/N\iin$.  For all three simulations, we use the time step size $\Delta
t=10^{-4}$.

>>>>

\input{preambles.tex}
\usepackage{showkeys}
\begin{document}

@@

Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
integral by first finding boundary data of $v$.  We assume that $\Omega$
is a simply-connected interior domain.  Similar formulas exist for
exterior domains, and for multiply-connected domains, $\bd\Omega$ is
simply decomposed into its different connected components.  The boundary
data of $v$ satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
Since $v$ is a holomorphic function and we have its boundary data, by
the Cauchy integral theorem we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.  A quadrature method to compute these Cauchy
integrals with a uniform error for all $x \in \Omega$ is presented in
Section~\ref{sec:bary}.

In equation~\eqref{eqn:cauchy}, $v(x)$ depends on the density function
$\eta \in \CC$, so we use the notation $v[\eta](x)$ to denote the
holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
the derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  Having
introduced this notation, the two components of the Stokes double-layer
potential are~\cite{bar-wu-vee2015}
\begin{equation}
  \begin{aligned}
    u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
             -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
    u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
         +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
  \end{aligned}
  \label{eqn:cauchyVelocity}
\end{equation}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation for the Gradient of the
Double-Layer Potential}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In addition to the velocity, we require a complex-valued representation
of the gradient of the velocity so that we can compute the shear stress
and the vorticity.  Each term of the gradient of the velocity field can
be written in terms of Cauchy integrals.  Taking the derivatives of
equation~\eqref{eqn:cauchyVelocity} with respect to $x_1$ and $x_2$, we
have 
\begin{equation}
\label{eqn:cauchyGradient}
  \begin{aligned}
    \pderiv{u_1}{x_1} &= +\Re (v'[\tau_1](x)) + 
      \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
      x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
    \pderiv{u_1}{x_2} &= - \Im (v'[\tau_1](x)) - 
      \Im (v''[y\cdot\eta](x)) + x_1\Im (v''[\eta_1](x)) - 
      \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
    \pderiv{u_2}{x_1} &= +\Re (v'[\tau_2](x)) - 
      \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
      x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
    \pderiv{u_2}{x_2} &= -\Im (v'[\tau_2](x)) - 
      \Re (v''[y\cdot\eta](x)) + x_1\Re (v''[\eta_1](x)) +
      \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
  \end{aligned}
\end{equation}
With these four expressions, the deformation tensor of the double-layer
potential, $\ssigma^D = \frac{1}{2} (\nabla \uu + \nabla \uu^T)$, is
written in terms of Cauchy integrals.  In addition, the vorticity is
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
 + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)).
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
\label{sec:bary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Equations~\eqref{eqn:cauchyVelocity} and~\eqref{eqn:cauchyGradient} show
that computing the Stokes velocity, shear stress, and vorticity hinge on
accurate quadrature methods for the Cauchy integral and its first two
derivatives as defined in equation~\eqref{eqn:cauchy}.  Even though the
trapezoid rule is spectrally accurate for a fixed $x \in
\Omega$~\cite{tre-wei2014}, its error depends on bounds of the
derivative of the integrand.  Therefore for a fixed resolution, as $x$
approaches $\bd\Omega$, causing the integrands to become more singular,
the error grows without bound.  Ioakimidis et al.~\cite{ioa-pap-per1991}
developed quadrature methods to compute Cauchy integrals and their
derivatives with an error bound that is independent of $x$.  Then,
Barnett et al.~\cite{bar-wu-vee2015} applied these quadratur emethods to
compute the Stokes double-layer potential representation of the
velocity~\eqref{eqn:stokesDLP}.  To compute the shear stress and
vorticity with the same accuracy, we extend the method by using
Barycentric quadrature methods for the second derivative of a Cauchy
integral.

We briefly summarize the Baryncentric quadrature method for computing
the velocity~\cite{bar-wu-vee2015}.  Then, we apply additional
quadrature methods to compute the gradient of the velocity so that we
can simulate erosion.  We present the quadrature for a simply-connected
interior domain $\Omega$, and we consider the target points $x \in
\Omega$ and $x \in \Omega^c$. Then, the method naturally extends to the
eroding geometry by applying the quadrature to each of its connected
component.  The method starts with an underlying quadrature rule, and we
use the spectrally accurate trapezoid rule.  Since the quadrature points
are uniformly distributed, the quadrature weights are $w_j = L/N$,
$j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.

Again, given a density function $\tau$, the boundary data of $v$ as
defined in equation~\eqref{eqn:laplaceComplex} can be found by applying
the Sokhotski-Plemelj jump relation~\eqref{eqn:SPrelation}.  The
boundary data differs if we are considering the interior problem ($x \in
\Omega$) or the exterior problem ($x \in \Omega^c$).  Therfore, for the
boundary data we use the notation $v^-$ for the interior problem and
$v^+$ for the exterior problem.  Rather than directly applying the
trapezoid rule to $v(x)$, we start with the identity
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
\end{align}
where we are considering the interior problem.  Since the integrand is
bounded as $x$ approaches $\bd\Omega$, we can apply the trapezoid rule
\begin{align}
  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0,
\end{align}
and the error is independent of $x$.  Rearranging for $v(x)$, we have
the quadrature formula
\begin{align}
  v(x) = \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}.
  \label{eqn:BaryvInterior}
\end{align}
Using a similar construction and letting $a$ be any point inside
$\Omega$, the Barycentric quadrature rule for the exterior problem is
\begin{align}
  v(x) = \frac{1}{x-a} 
    \frac{\sum\limits_{j=1}^N \frac{v^+(y_j)}{y_j - x}w_j}
    {\sum\limits_{j=1}^N \frac{(y_j - a)^{-1}}{y_j - x}w_j}.
  \label{eqn:BaryvExterior}
\end{align}

Similar constructions can be used to derive quadrature rules
for $v'(x)$.  For $x \in \Omega$, we have the identity
\begin{align}
  \int_{\bd\Omega} \frac{v^-(y) - v(x) + (y-x)v'(x)}{(y - x)^2} = 0,
\end{align}
and the integrand is bounded for all $x$.  Therefore, upon applying the
quadrature rule and rearranging for $v'(x)$, we have
\begin{align}
  v'(x) = \frac{\sum\limits_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
  \label{eqn:BaryvprimeInterior}
\end{align}
Using a similar construction, the Barycentric quadrature rule to compute
$v'(x)$ in $\Omega^c$ is
\begin{align}
  v'(x) = \frac{1}{x-a} \frac{\sum\limits_{j=1}^N
    \frac{v^+_j - v(x)}{(y_j - x)^2} w_j}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j - x} w_j}.
  \label{eqn:BaryvprimeExterior}
\end{align}
Note that the value $v(x)$ is required to compute $v'(x)$ for both the
interior and exterior case.  These are computed using the quadrature
methods in equations~\eqref{eqn:BaryvInterior}
and~\eqref{eqn:BaryvExterior}.

To compute the shear stress and vorticity, we require a Barycentric
quadrature rule for $v''(x)$.  Following the work of Ioakimidis et
al~\cite{ioa-pap-per1991} (see equation (2.12)), we mimick the
construction of the quadrature rule for $v(x)$ and $v'(x)$. We start
with the second derivative of the Cauchy integral theorem
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x).
\end{align}
For the interior case, $x \in \Omega$, we use the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n = 2,3,\ldots. \\
    \end{array}
  \right.
\end{align}
Combining this identity with the Cauchy integral representation of
$v''(x)$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
This integrand is constructed so that it is bounded for all $x \in
\Omega$, and applying the trapezoid rule, we have
\begin{align}
  0 \approx  \sum_{j=1}^{N} 
      \frac{2v^{-}(y_j) - v''(x)(y_j-x)^2 - 2v(x) - 2(y_j-x)v'(x)}
      {(y_j-x)^3} w_j,
\end{align}
where the accuracy is independent of $x$.  Solving for $v''(x)$, the
Barycentric quadrature rule for the second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
\end{align}
For the exterior case, $x \in \Omega^c$, we start with the identity
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x} dy. 
\end{align}
Combining this identity with the Cauchy integral representation of
$v''(x)$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
    \frac{2v^+(y) - 2v(x) - 2(y-x)v'(x) + (y-a)^{-1} (x-a) (y-x)^2 v''(x)}
    {(y-x)^3}.
\end{align}
As in the interior case, the integrand is chosen so that it is bounded
for all $x \in \Omega$.  Therefore, after applying the trapezoid rule
  and solving for $v''(x)$, we have the Barycentric quadrature rule
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
\end{align}
Similar to the quadrature rule for $v'(x)$ requring the value $v(x)$,
the quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$.
Both these quantities are computed using the quadrature rules in
equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
and~\eqref{eqn:BaryvprimeExterior}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Streamlines and Tortuosity}
\label{s:streamlines}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo[inline]{Dump of earlier section for now ... need to fix how this
is worked into the section}
Having developed numerically accurate methods to compute the velocity
$\uu$ at points close to the bodies, we are able to compute the
trajectories of particles passing through an eroded body.  To find the
trajectory governed by equation~\eqref{eqn:trajectories}, we use the
fourth-order explicit Runge-Kutta method with a fixed time step size.
Since our method is both high-order in time and space, we are able to
simulate dynamics very close to the eroding bodies (Figure~\ref{fig:}
\todo[inline]{reference a figure or two from the results section)}.
Resolving the flow in these small velocity regions is essential to
accurately describe anomalous diffusion and
mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a single eroding body close to a solid wall.  To compare our
results with a similar numerical experiment performed by Mitchell and
Spagnolie~\cite{mit-spa2017}, rather a pressure drop boundary condition,
we impose the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
on the outer wall.  In their experiment, Mitchell and Spagnolie place
the center of the eroding body $1.5$ times the body's radius above the
solid wall.  By using the numerical integration scheme described in
Section~\ref{s:method}, the eroding body can be placed much closer to
the solid wall.  In the following experiments, we consider an eroding
body that is initially a circle of radius $r=0.4$ and is placed near the
no-slip wall at $y=-1$.  We discretize the eroding body with
$N_\iin=256$ discretization points, and the center of the eroding body
is initially chosen so that the distance between the body and the solid
wall are $h/2$, $h/4$, and $h/10$, where $h = 2\pi r/N_\iin$.  For all
three simulations, we use the time step size $\Delta t=10^{-4}$.
